### 2018-09-23 ApproxComp/TKDE/sec-beyond.tex

\section{Beyond Query and Data Approximation}
\label{sec-beyond}

@@

We have seen that sampling helps to achieve a balance between efficiency and effectiveness for approximate query processing~\cite{ChaudhuriDK17,Mozafari17,Kraska17,GarofalakisG01} and link prediction~\cite{DuanAMHH16,DuanMAMH17}},
and other techniques such as incremental computation~\cite{Reps96,FanLMTWW10,rankicde2018}, distributed computing~\cite{MaCHW12,FanXWYJZZCT17}, and system techniques~\eg caching~\cite{WangLMNT18}, new hard ware~\cite{ArulrajPD15,iccd2018} can also be unitized for big data analytics, and can even be combined for designing query and data approximation techniques for big data analytics.

>>>>

\section{Beyond Approximation Techniques}
\label{sec-beyond}

@@

We have seen that sampling helps to achieve a balance between efficiency and effectiveness for approximate query processing~\cite{ChaudhuriDK17,Mozafari17,Kraska17,GarofalakisG01} and link prediction~\cite{DuanAMHH16,DuanMAMH17}},
and other techniques such as incremental computation~\cite{Reps96,FanLMTWW10,rankicde2018}, distributed computing~\cite{MaCHW12,FanXWYJZZCT17}, and system techniques~\eg caching~\cite{WangLMNT18}, hardware~\cite{AbergerLTNOR17,Han0Y18} can also be unitized for big data analytics, and can even be combined for designing query and data approximation techniques for big data analytics.

### 2018-09-23 ApproxComp/TKDE/sec-data.tex

Essentially, in our graph embedding, $d$ represents the number of communities. As the anomalous nodes are only determined by influential communities and nodes typically connect to a limited number of communities, the complete d-dimensions are unnecessary, and a limited number of communities suffice to ascertain anomalies. Thus, our dimension reduction technique (referred to as ($k+\beta$ reduction) only maintains ($k + \beta$)-dimensions for embedding of each node, where k is the maximum number of communities to connect, $\beta$ is to tolerate mistakes when determining the $k$ communities and is removed after the computation process. Here $k, \beta \ll d$, \eg $k = 10$ and $\beta = 2$ and $d=600$ for a network with $10^6$ nodes.

>>>>

Essentially, in our graph embedding, $d$ represents the number of communities. As the anomalous nodes are only determined by influential communities and nodes typically connect to a limited number of communities, the complete d-dimensions are unnecessary, and a limited number of communities suffice to ascertain anomalies. Thus, our dimension reduction technique (referred to as $k+\beta$ reduction) only maintains ($k + \beta$)-dimensions for embedding of each node, where k is the maximum number of communities to connect, $\beta$ is to tolerate mistakes when determining the $k$ communities and is removed after the computation process. Here $k, \beta \ll d$, \eg $k = 10$ and $\beta = 2$ and $d=600$ for a network with $10^6$ nodes.
